Mathematical Formulation of Projection Problem

### 2025-02-28 docs/logbook.tex
Updated logbook

>>>>

	\begin{MeetingMinutes}{Wed 26/02/2025}{u7013004}
		Have explored many many options for the physics simulation. I will list them out. The aim is to get good data by Friday. I will aim by tonight to have tried various options and have thought about which one is best.
		The options are:
		\begin{enumerate}
			\item NVIDIA Omniverse - pros: minimal effort to set up inflatable, can set up scene easily, cons: unsure how mesh would be extracted, I will need access to Pranav's computer
			\item Feather - pros: physics looks robust, easily usable interface, should be easily to extract mesh and it's in C++, can simulate interactions, cons: will need to manually set up environment, port to Blender and render there, requires Linux
			\item Q-Minh: pros: good interface, physics looks good, should be easy to extract mesh, in C++, cons: need to port to Blender
			\item \sout{liujustin53: unknown, will have to try} BAD!
			\item PBS-soft-body (ETH): can interact with rigid body if the rigid body is in the scene and not moving
			\item PBDTaichi: Python, pretty basic, can't handle collisions with other objects
		\end{enumerate}

		FML. Feather can only work on OpenGL 4.3 so I'll try on Windows at home.

		Can also ask Jiahao about the apt stuff for libgl and other RandR (RandR library and headers were not found).

		Can use the PBAToolkit in Python, so that should be doable on Mac. Same with some of the other ones.

		The Feather one, I have almost no hope for. I can try to run it on the GPU but the OpenGL is so far behind.
	\end{MeetingMinutes}

	\begin{MeetingMinutes}{Thu 27/02/2025}{u7013004}
		This really sucks right now bruh. I am bumping into dead ends and I wonder if the only thing I can use is Pranav's computer atm.
		Going to try vcpkg again for Feather and Q-Minh (he replied and said he hasn't ported it over to Python yet but can do it next week).
		In the meantime, I can try liujustin53, PBS-soft-body (ETH).
		Verdict: liujustin53 can't do collisions.
	\end{MeetingMinutes}

	\begin{MeetingMinutes}{Fri 28/02/2025}{u7013004}
		Ok, need to ask if I can somehow use a computer with a GPU. If not, rent one?
		NVIDIA Omniverse has everything, I just need to be able to use it.

		My options otherwise are PBDTaichi, PBS-soft-body, and Feather.
		All can do volume preservation.\\

		Feather is super slow but can do bending and length constraints, and can handle collisions with other objects. Investigate solver iteration.

		PBDTaichi has bending and length constraints, but cannot handle collisions with other objects.

		PBS-soft-body has length and friction constraints, can handle collisions with static objects in the scene, cannot handle collisions with other objects.

		For now, I need some really basic data to get the pipeline working.

		Discussion with Steve: he'll ask IT, I will generate a simple example in Blender first.

### 2025-02-28 docs/projection.tex
Updated logbook

Though this can be confusing, if we take a step back, conceptually, the components of our bi-level optimisation are:
$$
\begin{array}{ll}
    \underset{}{\text{minimize}} &  \text{difference between current points $V^*$ and target} \\[0.5em]
  \text{subject to} & V^* = \text{argmin} \; \text{projection of current points onto intended shape} \\[0.5em]
  & \hphantom{y =} \text{subject to} \;  \text{volume constraint}
\end{array}
$$

>>>>

Though this can be confusing, if we take a step back, conceptually, the components of our bi-level optimisation are:
$$
\begin{array}{ll}
    \underset{}{\text{minimize}} &  \text{error between projected mesh points $V^*$ and target} \\[0.5em]
  \text{subject to} & \text{projected mesh points } V^* = \text{argmin} \; \text{nearest points to existing mesh} \\[0.5em]
  & \hphantom{y =} \text{subject to} \;  \text{volume constraint}
\end{array}
$$
